Supplemental Material for \\ Helixer: Cross-species Gene Annotation of Large Eucaryotic Genomes Using Deep Learning

### 2020-04-22 paper/supplements.tex
stuff

\documentclass{article}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage{natbib}

@@

\title{Supplemental Material for \\ Helixer: Cross-species gene annotation of large eucaryotic genomes using deep learning}

@@

\date{}
\maketitle

@@

\begin{table}[!h]
\renewcommand\thetable{S1}
\centering
\begin{tabular}{@{}ll@{}}
\hline
Parameter & Value \\ [0.5ex]
\hline
Layers & 4\\
Units per layer & 256\\
Learning rate & 1e-4\\
Optimizer & Adam\\
\hline
\end{tabular}
\caption{}
\label{suptab:params}
\end{table}

\newpage
\section{Overlapping evaluation by species}
\label{sec:overlapping}
\begin{figure}[!h]
% \centerline{\includegraphics[height=0.01\paperheight]{images/overlapping/animals_overlapping}}
\caption{Caption, caption.}\label{fig:animals_overlapping}
\end{figure}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage{natbib}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}

@@

\title{Supplemental Material for \\ Helixer: Cross-species Gene Annotation of Large Eucaryotic Genomes Using Deep Learning}

@@

\date{}
\maketitle
\tableofcontents

\begin{table}[!h]
\renewcommand\thetable{S1}
\centering
\begin{tabular}{@{}ll@{}}
\hline
Parameter & Value \\ [0.5ex]
\hline
Layers & 4\\
Units per layer & 256\\
Learning rate & 1e-4\\
Optimizer & Adam\\
\hline
\end{tabular}
\caption{All hyperparameters used for the }
\label{suptab:params}
\end{table}

\newpage
\section{Overlapping Evaluation by Species}
\label{sec:overlapping}
\begin{figure}[!h]
% \centerline{\includegraphics[height=0.01\paperheight]{images/overlapping/animals_overlapping}}
\caption{Caption, caption.}\label{fig:animals_overlapping}
\end{figure}

@@
